Contextual Combinatorial Cascading Bandits

### 2016-01-09 contextual combinatorial cascading bandits.tex
update introduction

Now personalized recommendation is a basic feature of websites to improve user satisfaction by providing attractive content to meet specific user's need. Personalization includes storing user features and historical information, managing content set, analysis of user behaviors and providing suitable content to the user. Usually, both users and content are represented by feature sets. User features may contain basic attributes, like age, gender and nationality, and historical behaviors. Content features may contain categories and descriptive information. Because the views of different users on the same content can vary significantly, exploration and exploitation have to be exercised at an individual level and be able to cross different contents.

In real applications, the cascade model is popular to describe user behaviors in recommendation systems. When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item. The items before the selected one are not attractive and the items after the selected one are unobserved. Also in networking routing problem, if we want to check a path from source to end to confirm whether it is blocked, we can just stop checking when meeting a blocked edge. The cascade model is useful to describe such kind of partial-observation problem.

Stochastic online learning with combinatorial actions has been studies with semi-bandit feedback \cite{chen2013combinatorial}.

>>>>

Now personalized recommendation is a basic feature of websites to improve user satisfaction by providing attractive content to meet specific user's need. Personalization includes storing user features and historical information, managing content set, analysis of user behaviors and providing suitable content to the user. Usually, both users and content are represented by feature vectors. User features may contain basic attributes, like age, gender and nationality, and historical behaviors. Content features may contain categories and descriptive information. Because the views of different users on the same content can vary significantly, exploration and exploitation have to be exercised at an individual level and be able to cross different contents.

In real applications, the cascade model is popular to describe user behaviors in recommender systems. When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item. The items before the selected one are not attractive and the items after the selected one are unobserved. Also in networking routing problem, to determine whether a path is blocked, we check from the source to the end and can stop when meeting a blocked edge without need of knowing states of every edge in the path. In both of the two applications, we the feedback of items before some threshold, which is that user selects one item in recommender system and meeting a blocked edge in network routing. We call this kind of feedback as {\it cascading feedback}.

Motivated by the above challenges, we develop an approach called {\it contextual combinatorial cascading bandits}. This is a general framework which can describe many applications besides the above two applications.

The main contributions of this paper can be listed as follows: (1) We propose a general framework called contextual combinatorial cascading bandit that can address recommendation problem and network routing problem; (2) We propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{T})$ for $T$ rounds; (3) We evaluate this algorithm on synthetic data, recommendation data and network routing data and the results show that our algorithm is effective.

%Stochastic online learning with combinatorial actions has been studied with semi-bandit feedback \cite{chen2013combinatorial}.
